RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-02-18 paper.tex
working

Kandel's interview study points out the typical ``explore'',
``model'', ``report'' cycle~\cite{Kandel:2012:EDA}. RCloud seeks to
reduce the impedance mismatch. Kandel et al point out that larger teams
are becoming more common in data analysis, that supporting
collaboration is a difficult and important problem, and that
sharing and versioning of data sources and artifacts was hindered
by technology.  ``We found that analysts typically did not share scripts
with each other. Scripts that were shared were disseminated similarly to
intermediate data: either through shared drives or email.
Analysts rarely stored their analytic code in source control.''
Their work points to the need for better technology to support
these aspects of data analysis in teams.

Heer and Agarwala identify a large number of design considerations for
collaborative visual analytics~\cite{Heer:2008:DCF}. \emph{Starring},
the system for signaling interest in notebooks, described in
Section~\ref{sec:starring}, addresses social-psychological incentives,
recommendation, and voting and ranking. RCloud's integrated deployment
mechanism, described in Section~\ref{sec:deployment}, addresses cost of
integration, content export, presentation and view sharing. Notebooks,
and the integrated version control system for them, described in
Section~\ref{sec:notebooks}, addresses modularity and granularity, and
artifact histories.

Our work has been inspired or has benefited from other modern technologies
to improve the data analysis environments and processes, such as RStudio,
R packages such as Markdown, knitr and Shiny, and iPython notebooks, to name a few.  % explain

@@

% limitations
Previous studies have pointed out frequent difficulties in the
achieving production-level flexibility, scalability and maintainability
with experimental code created by data analysts.  These properties cannot
be ensured by any programming environment, but a reasonable approach in
general is to provide suitable tools that make it easier for well-intentioned
programmers to adopt such practices.

% security issues

\section{Conclusions}

>>>>

Kandel's interview study points out the typical ``explore'',
``model'', ``report'' cycle~\cite{Kandel:2012:EDA}. There
are many discontinuities in this cycle that cost time and
effort to overcome.  RCloud seeks to reduce this impedance
mismatch. Kandel et al also point out that larger teams are
becoming more common in data analysis, that supporting
collaboration is a difficult and important problem, and that
sharing and versioning of data sources and artifacts is hindered
by current technology in practice. ``We found that analysts typically
did not share scripts with each other. Scripts that were shared were
disseminated similarly to intermediate data: either through shared
drives or email. Analysts rarely stored their analytic code in
source control.'' Their work points to the opportunity for better
technology to support collaboration and sharing by data analysis teams.

Heer and Agarwala identify many design considerations for
collaborative visual analytics~\cite{Heer:2008:DCF}. \emph{Starring},
the system for signaling interest in notebooks, described in
Section~\ref{sec:starring}, addresses social-psychological incentives,
recommendation, and voting and ranking. RCloud's integrated deployment
mechanism, described in Section~\ref{sec:deployment}, addresses cost of
integration, content export, presentation and view sharing. Notebooks,
and the integrated version control system for them, described in
Section~\ref{sec:notebooks}, address modularity and granularity, and
artifact histories.

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. iPython \cite{Perez:2007:ISI:1251563.1251831}
shares many of our goals...

@@

% limitations
Previous studies have pointed out difficulties in achieving production-level
flexibility, scalability and maintainability with experimental code created
by data analysts. These properties cannot be ensured by any programming environment,
but suitable tools can help well-intentioned analysts and programmers to create
robust applications with less effort.
